Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-23 paper.tex
use microtype
fix description of private key (scalar) clamping; staying < 2^255-19 is not a relevant requirement

\documentclass[12pt, a4paper, twocolumn]{article}
\usepackage{xurl}
\usepackage[sort&compress]{natbib}
\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
\usepackage{amsmath} % Add this line to define the \text command
\usepackage{titlesec}
\usepackage[skip=10pt]{parskip}
\usepackage{enumitem}

@@

Unfortunately, private keys have to be derived by hashing the seed and manipulating the bits. RFC\-8032~\cite{RFC8032} specifies that of the 32 byte private key:

\begin{itemize}[label=\textendash, itemsep=-0.5em]
  \item Bits 0, 1, 2:  set to 0, ensuring that the key is a multiple of 8 and avoiding small subgroup attacks.
  \item Bit 254: set to 1, to ensuring the Montgommery ladder computation used in scalar multiplication runs in constant time.
  \item Bit 255: set to 0, ensuring the key is in the range of the field order ($2^{255} - 19$).
\end{itemize}

By definition the key space for Ed25519 is non-linear.

>>>>

\documentclass[12pt, a4paper, twocolumn]{article}
\usepackage{microtype}
\usepackage{xurl}
\usepackage[sort&compress]{natbib}
\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
\usepackage{amsmath} % Add this line to define the \text command
\usepackage{titlesec}
\usepackage[skip=10pt]{parskip}
\usepackage{enumitem}

@@

Unfortunately, private keys have to be derived by hashing the seed and manipulating the bits.
RFC\-8032~\cite{RFC8032} specifies that of the 32-byte ``expanded'' private key:
\begin{itemize}[label=\textendash, itemsep=-0.5em]
\item Bits 0, 1, 2 are set to 0, ensuring that the key is a multiple of 8, thus avoiding small-subgroup attacks.
\item Bit 255 is set to 0, to ensure that the key is less than the order of the elliptic-curve group.
\item Bit 254 is to 1, to ensure that the Montgomery ladder computation used in scalar multiplication runs in constant time.
\end{itemize}
So, by definition, the key space for Ed25519 is non-linear.
